Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-15 tsibbletalk.Rmd
minor tweak

A group of cohesive observational units measured over time typically form one temporal data set. Ensemble graphics [@unwin_ensemble_2018] that bundle multi-views for a data set together, are essential for exploring and mining temporal data in multi-facets. Adding interactivity, such as linked brushing via common observations and wrapping by time, can accelerate this process.

@@

Close to the heart of the \CRANpkg{tsibbletalk} package is blending the best bits from \CRANpkg{tsibble} and \CRANpkg{crosstalk}.

>>>>

A group of cohesive observational units measured over time typically form one temporal data set. Ensemble graphics [@unwin_ensemble_2018] that bundle multi-views for a data set together, are essential for exploring and mining many different aspects of temporal data. Adding interactivity, such as linked brushing via common observations and wrapping by time, can accelerate this process.

@@

Close to the heart of the \CRANpkg{tsibbletalk} package is blending the best bits from \CRANpkg{tsibble}, \CRANpkg{crosstalk}, and \CRANpkg{plotly}.
